\documentclass[12pt, journal, onecolumn]{IEEEtran}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows, positioning}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\lstset{
  basicstyle=\ttfamily\footnotesize,
  breaklines=true,
  frame=single,
  language=JavaScript,
  keywordstyle=\color{blue},
  stringstyle=\color{red},
  commentstyle=\color{green!50!black},
  showstringspaces=false,
  numbers=left,
  numberstyle=\tiny\color{gray},
  stepnumber=1,
  numbersep=5pt
}

\begin{document}

\title{Rural Gyan Platform: An AI-Integrated Full-Stack Virtual Learning System for Rural India}

\author{
    \IEEEauthorblockN{Neha Gaikwad, Meghana Prathipati, Saylee Shelar} \\
    \IEEEauthorblockA{\textit{Department of Computer Engineering} \\
    \textit{Ajeenkya DY Patil University (ADYPU)}\\
    Pune, Maharashtra, India}
}

\maketitle

\begin{abstract}
The digital divide in education remains a critical challenge for emerging economies, particularly in rural India, where infrastructural and linguistic barriers impede access to quality learning. This paper explores the design, architecture, and implementation of ``Rural Gyan Platform,'' a comprehensive, full-stack educational system tailored to mitigate these challenges. Built utilizing a modern technology stack—comprising React.js for the client side, Node.js and Express.js for the server infrastructure, MongoDB for robust data persistence, and Socket.io for low-latency real-time communication—the platform delivers a robust learning ecosystem. It directly addresses the constraints characteristic of rural Indian environments, such as low bandwidth availability, linguistic isolation, and an unmet need for highly interactive, synchronous digital tools. The system features a sophisticated role-based access model serving Administrators, Teachers, and Students through customized dashboards. A core innovation is the integrated WebRTC-based peer-to-peer virtual classroom, which operates efficiently on constrained networks by eliminating intermediary relay servers. Furthermore, the platform incorporates a multimodal AI Tutor powered by Google's Gemini large language model, facilitating personalized learning experiences. To bridge the linguistic divide, seamless bilingual support (English and Hindi) is embedded using the react-i18next framework alongside live automated translations via Google's translation capabilities. The entire system is containerized using Docker, ensuring highly decoupled, resilient, and scalable deployment pipelines.
\end{abstract}

\begin{IEEEkeywords}
WebRTC, Artificial Intelligence, Educational Technology, Socket.io, React.js, Full-Stack Development, Peer-to-Peer Networks.
\end{IEEEkeywords}

\section{Introduction}
The democratization of education through digital platforms has revolutionized pedagogical methodologies globally. However, the manifestation of this digital transformation is markedly disproportionate. In the context of India, the digital divide poses a profound systemic challenge. With a rural population exceeding 650 million individuals, technological penetration remains sub-optimal. Recent statistical analyses reveal that broadband penetration in rural sectors hovers approximately at 27\%, juxtaposed against significantly higher urban metrics. Furthermore, linguistic barriers severely restrict the efficacy of standard digital learning platforms. While Hindi and various regional languages constitute the primary medium of communication and instruction for the vast majority of the rural populace, empirical data highlights that approximately 92\% of available digital educational content is presented in English.

When analyzing existing market solutions, several architectural and functional limitations become overtly apparent when deployed in resource-constrained environments. Industry-standard platforms exhibit the following critical constraints:
\begin{itemize}
    \item \textbf{Google Classroom:} Functions fundamentally as an asynchronous assignment and document management system. It lacks native, integrated WebRTC for concurrent video conferencing and natively integrated collaborative whiteboarding.
    \item \textbf{Moodle:} Traditionally architected as a monolithic PHP application, it relies heavily on external, third-party plugins to achieve modern synchronicity, frequently leading to bloated installations and sub-optimal runtime performance constraints.
    \item \textbf{Zoom Education:} While excelling in robust video delivery, its architecture intrinsically routes streams through centralized relay servers. This relay-based topology necessitates higher baseline computational bandwidth and fails to optimize local peer connections inherent in decentralized rural mesh environments.
    \item \textbf{Khan Academy:} Delivers exemplary modular content yet operates exclusively in an asynchronous paradigm, devoid of real-time teacher-student immediate interactive feedback loops.
\end{itemize}

To address this substantive gap, we present the \textit{Rural Gyan Platform}. Our contributions encompass the complete end-to-end architectural engineering and implementation of an integrated educational ecosystem. Specifically, we have successfully synthesized low-latency WebRTC peer-to-peer networking, real-time advanced Collaborative Whiteboarding, Live Bilingual Captions (English-Hindi), and a Multimodal AI Tutor within a single, cohesive, and optimized application context.

\section{System Architecture}
The Rural Gyan Platform operates on an optimized three-tier architectural paradigm, strictly decoupling presentation, application logic, and data persistence layers to maximize maintainability and elastic scalability.

\subsection{Architectural Topology}
The \textbf{Client Tier} is an isomorphic Single Page Application (SPA) constructed utilizing React.js, responsible for managing complex frontend state and optimizing browser-side rendering cycles. The \textbf{Application Tier} functions as a RESTful API server authored in Node.js utilizing the Express.js framework, managing routing, business logic, asynchronous non-blocking I/O operations, and integrating third-party service hooks. The \textbf{Data Tier} leverages MongoDB Atlas, a highly available, fully managed NoSQL document database, allowing dynamic schemas crucial for diverse educational metrics. 

\begin{figure}[htbp]
\centering
\begin{tikzpicture}[
    node distance=2.8cm,
    auto,
    comp/.style={rectangle, draw, fill=blue!10, text width=7.5em, text centered, rounded corners, minimum height=3.5em, font=\footnotesize},
    db/.style={cylinder, draw, shape border rotate=90, aspect=0.25, fill=green!10, text width=6em, text centered, minimum height=4em, font=\footnotesize},
    api/.style={ellipse, draw, fill=red!10, text width=6em, text centered, minimum height=3em, font=\footnotesize},
    line/.style={draw, -latex', thick}
]

    % Nodes
    \node [comp] (client) {\textbf{Client Tier} \\ React.js SPA \\ React Native};
    \node [comp, right=of client] (server) {\textbf{Application Tier} \\ Express.js API \\ Socket.io Server};
    \node [db, right=of server] (database) {\textbf{Data Tier} \\ MongoDB Atlas \\ (NoSQL)};
    
    \node [api, above=1cm of server] (gemini) {Google Gemini \\ 2.0 API};
    \node [api, above=1cm of client] (webrtc) {WebRTC P2P \& \\ STUN Servers};
    
    % Paths
    \path [line, <->] (client) -- node[above, font=\scriptsize] {HTTPS /} node[below, font=\scriptsize] {WebSockets} (server);
    \path [line, <->] (server) -- node[above, font=\scriptsize] {Mongoose/TCP} (database);
    \path [line, <->] (server) -- node[right, font=\scriptsize] {AI Prompts} (gemini);
    \path [line, <->] (client) -- node[left, font=\scriptsize] {Signaling} (webrtc);

\end{tikzpicture}
\caption{System Architecture Diagram detailing the Three-Tier Model with specific technology boundaries and external API hooks.}
\label{fig:architecture}
\end{figure}


\subsection{Real-time Communication Infrastructure}
To facilitate instantaneous synchronization across clients, WebSocket protocols are abstracted via \texttt{Socket.io}. The system strictly scopes event traffic by compartmentalizing namespaces. A primary namespace orchestrates all virtual classroom events (peer signaling, chat logic, whiteboard telemetry), while a dedicated \texttt{/tutor} namespace securely handles all asymmetric asynchronous communication pertaining to the AI Tutor queries to prevent event pollution and collision.

\subsection{Security and Middleware Configuration}
Transport layer security and application-level authorization operate utilizing JSON Web Tokens (JWT). The platform dictates a dual-token strategy involving short-lived cryptographic Access Tokens and long-lived Refresh Tokens securely stored in HttpOnly cookies and local mechanisms. Passwords undergo rigorous hashing using \texttt{bcrypt} configured with a work factor (salt rounds) of 12 prior to persistence. Access to protected API endpoints traverses a robust custom Role-Based Access Control (RBAC) middleware verifying cryptographic signatures and explicit role claims (admin, teacher, student). 

Further infrastructural security includes rigorous rate-limiting parameterized via \texttt{express-rate-limit} restricted to 100 requests per 15-minute window per IP configuration to mitigate brute-force vectors and volumetric Distributed Denial-of-Service (DDoS) phenomena. \texttt{Helmet.js} standardizes imperative HTTP security headers to counteract Cross-Site Scripting (XSS) and clickjacking logic, while stringent Cross-Origin Resource Sharing (CORS) whitelists encapsulate domain access explicitly.

\subsection{Docker-Based Orchestration and Containerization}
The full-stack application lifecycle is managed via Docker and Docker Compose, achieving complete environmental parity across development, staging, and production. The orchestrated matrix comprises independent containers for MongoDB 6.0, the Node.js API server, the React.js client build compilation, and an Nginx reverse proxy routing external ingress traffic optimally. Deployment mechanics target Vercel or Netlify for global Content Delivery Network (CDN) edge distribution of the compiled static frontend, alongside Render or Railway PaaS instances for persistent backend Node.js compute environments.

\section{Role-Based Dashboard System}
Interface engineering necessitates distinct contextual environments strictly bound to user authorizations, implemented utilizing an immersive Tailwind CSS framework characterized by a cyberpunk-inspired dark mode thematic, including high-contrast scanline effects, discrete glitch text animations on state transit, and \texttt{font-mono} typographies evoking a modern, computational interface logic.

\subsection{Admin Dashboard}
Administrators wield overarching mutative capabilities. The dashboard renders high-level macro analytics, parsing the MongoDB schemas for quantitative aggregations (total teachers, student volumes, concurrent active sessions, and anomalous activity logs). It features full Create, Read, Update, and Soft-Delete (CRUD) capabilities via a toggle-status heuristic (toggling the \texttt{isActive} boolean schema property rather than destructive atomic deletions) for Teacher and Student entities, strictly tracking institutional enrollment numerics.

\subsection{Teacher Dashboard}
The Teacher portal serves as the academic operational nexus. Instructors coordinate asynchronous content upload workflows within the \textit{Materials management} utility, while actively utilizing \textit{Class management} to schedule, initiate, and forcefully terminate synchronous Live Virtual Classes. The \textit{Quiz management} system empowers instructors to craft assessments comprising classical Multiple-Choice Questions (MCQs) alongside sophisticated Algorithmic Coding evaluations utilizing sandboxed parameters. Further administrative tools encompass \textit{Allocated subjects} indexing, \textit{Performance analysis} arrays rendering continuous student grading data, and \textit{Weekly timetable} chronological mappings.

\subsection{Student Dashboard}
Students interact with a streamlined experiential environment. Direct integration is provided for fetching ongoing \textit{Virtual classes} and subsequent one-click joins. The interface provisions immediate access to deposited materials, continuous \textit{Quiz taking} facilities bounded by explicit temporal windows, chronologically mapped Timetable tracking, and integrations for both the Multimodal \textit{AI Tutor} overlay and the integrated Virtual Code Editor.

\section{Virtual Classroom Subsystem (Core Innovation)}
Addressing bandwidth deficits demands the localized routing logic inherent to WebRTC, explicitly rejecting centralized Selective Forwarding Unit (SFU) or Multipoint Control Unit (MCU) server dependencies that historically plague low-bandwidth connections.

\subsection{WebRTC Peer-to-Peer implementation}
The topology implements a complete Peer-to-Peer (P2P) mesh network architecture executing over the WebRTC protocol stack, programmatically managed via the \texttt{simple-peer} wrapper library. Traversal Using Relays around NAT (STUN) server mechanisms negotiate necessary public IP and port mappings. Reliable Google STUN instances (\texttt{stun.l.google.com:19302}, \texttt{stun1}, \texttt{stun2}) operate precisely to resolve host candidates asynchronously.

\subsection{Socket.io Signaling Mechanism}
Real-time session negotiation utilizes Socket.io to establish preliminary signaling handshakes. Crucial events include:
\begin{itemize}
    \item \texttt{join-virtual-class}: Initiates the socket join room directive alongside identifying metadata.
    \item \texttt{video-offer} \& \texttt{video-answer}: Transmits underlying Session Description Protocol (SDP) payloads.
    \item \texttt{ice-candidate}: Exchanging localized Interactive Connectivity Establishment candidates.
    \item \texttt{leave-virtual-class} \& \texttt{participant-left}: Triggering peer destruction routines upon disconnects.
\end{itemize}

\begin{lstlisting}[caption=Socket.io WebRTC Signaling Event Handler]
io.on('connection', socket => {
  socket.on('join-virtual-class', (roomId, userId) => {
    socket.join(roomId);
    socket.to(roomId).emit('participant-joined', userId);
  });
  
  socket.on('video-offer', (offer, roomId, targetPeerId) => {
    socket.to(targetPeerId).emit('video-offer', offer, socket.id);
  });
});
\end{lstlisting}

\subsection{Screen Sharing and Live Captions}
The Screen Sharing mechanism executes track substitution locally dynamically executing \texttt{RTCRtpSender.replaceTrack()} logic securely over all active peer connections without necessitating session renogitation.

Live Speech-to-Text capability leverages the implicit Web Speech API (\texttt{webkitSpeechRecognition}). Local microphone buffers recognize English phonetics, subsequently initiating an asynchronous HTTP request directed toward the free Google Translate API endpoint (\texttt{translate.googleapis.com/translate\_a/single}). The algorithm yields translated Hindi strings, which are immediately broadcast out to the room channel via the \texttt{caption-update} socket event string to overlay on recipient frames globally.

\subsection{Telemetry, Attendance, and Lifecycle Controls}
The \texttt{VirtualClass} Mongoose configuration governs lifecycle statuses leveraging an Enum mapping (\texttt{scheduled}, \texttt{live}, \texttt{ended}, \texttt{cancelled}). Concurrency relies upon auto-generated \texttt{meetingId} cryptographics paired securely with a session-specific \texttt{meetingPassword}.

Authoritative controls empower the Instructor explicitly via socket payloads routing to targeted socket IDs (e.g., \texttt{teacher-mute-student}, \texttt{teacher-video-off-student}). Hand elevation utilizes basic Boolean toggle emitters (\texttt{raise-hand}, \texttt{lower-all-hands}).

Attendance automation operates distinctly, triggering upon joining and periodically verifying presence markers via RESTful API \texttt{PATCH /:id/attendance/mark} hooks, yielding an exportable CSV buffer string upon class conclusion via the \texttt{end-class-broadcast} termination event gracefully redirecting client routing trees.

\section{Collaborative Whiteboard}
The integration features an HTML5 \texttt{<canvas>} synchronized globally via discrete coordinate transmission paths.
All drawing events conditionally execute behind an \texttt{isTeacher} middleware conditional ensuring unidirectional graphic flow.
Toolsets encompass variable vector mechanisms (pen, 7-color palettes, defined 1-10px line radii) and eraser functionality inherently achieving non-destructive removal utilizing native Canvas \texttt{destination-out} global composite operational flags.
Socket telemetry limits to \texttt{whiteboard-draw} (encoding Cartesian $x, y$ sets, hex colors, and coordinate boundaries) and global wiping arrays. Static exportation outputs raw Base64 image encoding dynamically via \texttt{canvas.toDataURL()} routed safely into standard anchor download elements. Client perspectives are implicitly locked within a "View Only - Teacher is drawing" localized overlay constraint.

\section{AI Tutor System}
Digital personalization involves integration with the robust Google Gemini 2.0 Flash multimodal language model (\texttt{gemini-2.0-flash}) orchestrated utilizing the \texttt{@google/generative-ai} SDK within Node.js.

\subsection{Architecture and Namespace}
Real-time dialogue operates exclusively over the strictly partitioned \texttt{/tutor} Socket.io namespace to ensure isolation from primary WebRTC bandwidth utilizing identical JWT middleware authorization arrays.

\begin{lstlisting}[caption=Gemini 2.0 Promisified Integration]
const { GoogleGenerativeAI } = require('@google/generative-ai');
const genAI = new GoogleGenerativeAI(process.env.GEMINI_KEY);
const model = genAI.getGenerativeModel({ model: "gemini-2.0-flash" });

async function processPrompt(multimodalData) {
   const result = await model.generateContent(multimodalData);
   const response = await result.response;
   return response.text();
}
\end{lstlisting}

\subsection{Multimodal Input Capabilities}
Beyond raw textual arrays, students are empowered to interact multidimensionally. PDF document parsing executes natively via the \texttt{pdf-parse} library, extracting valid string data. Word documents (.docx) utilize binary XML parsing heuristics constructed via \texttt{mammoth}, whereas image-based text queries pass through \texttt{Tesseract.js} optical character recognition (OCR) arrays mapping visual arrays to analyzable prompt contexts seamlessly.

\subsection{Translation Translation Pipeline}
Asymmetric translation occurs recursively across the dialogue cycle. Primary inputs, specifically constructed in native Hindi, utilize a pre-processing step hitting the Google Translate infrastructure normalizing raw parameters explicitly into systemic English structures. The English parameter string queries the Gemini framework producing the instructional response. The response dynamically reverses the pipeline ensuring authentic bi-lingual structural support immediately.

\subsection{Frontend Interactions}
Clients interact employing file limits optimized to 10MB capacities. Direct Voice Input leverages the native \texttt{MediaRecorder API} producing localized binary blobs sent strictly as transcription buffers. Responses execute within comprehensive paginated local history tracking architectures (50 queries bound by page) indexed cleanly on the MongoDB \texttt{AiChatHistory} dimensional model. UX optimizations include thumbs-up/down qualitative reactions, instantaneous copy-to-clipboard functionalities, fluid fullscreen expanding wrappers, and visual typing manifestation indicators masking query latency optimally.

\section{Quiz Management System}
Remote assessment capabilities operate comprehensively upon independent robust schemas encapsulating multidimensional test data vectors mapping Section blocks to specific Query nodes (MCQ alongside strictly-enumerated programmatic coding variations—JavaScript, Python, Java, C++, SQL).

Teacher configuration restricts exams within bounds configured by overarching absolute marks, per-query weighting factors, fixed numerical duration constants, defined \texttt{startTime} initialization events, and strict \texttt{endTime} cutoff triggers mapping natively to Unix epoch boundaries.

Execution parameters are inherently deterministic. The MCQ logical pathway calculates grading dynamically directly upon submission evaluating incoming target indexing strings natively against an invisible \texttt{correctAnswer (0-3)} baseline yielding immutable arrays dictating \texttt{marksObtained}, derived \texttt{percentage}, and temporal delta values recording overall \texttt{timeTaken}. Coding problems yield distinct Input/Output programmatic pairs awaiting sandboxed analytical comparison blocks.

\section{Bilingual Support}
Bridging fundamental language disparities within regional localities functions directly utilizing \texttt{react-i18next} architecture. The framework fundamentally sidesteps performance degradation regarding asynchronous external HTTP translation downloads by storing complex hierarchical JSON dictionary mappings internally bounding English and Hindi structural keys directly within memory maps during compilation cycles.

More than 80 independent functional translation maps encapsulate every critical node present actively on the DOM encompassing Auth patterns, discrete Dashboard menus, Virtual Class notifications, AI interfaces, and Profile configurations. A persistent, globally scoped Language Switcher governs current state parameters mutating context cleanly enforcing Hindi logic instantly across parameters spanning navigational targets natively to the overarching institutional tagline translated perfectly to \textit{"डिजिटल शिक्षा के माध्यम से भारत के भविष्य को सशक्त बनाना"}.

\section{Security Implementation}

Application security maintains zero-trust standards globally. 
\begin{lstlisting}[caption=Authorization Middleware using JWT]
const jwt = require('jsonwebtoken');

const auth = (req, res, next) => {
  try {
    const token = req.header('Authorization').replace('Bearer ', '');
    const decoded = jwt.verify(token, process.env.JWT_SECRET);
    req.user = decoded;
    next();
  } catch (error) {
    res.status(401).send({ error: 'Please authenticate.' });
  }
};
\end{lstlisting}

Password mechanisms specifically hash leveraging \texttt{bcryptjs} and robust mathematical salt rounds equivalent to 12 ensuring defense vectors against rapid brute force or rainbow table computational arrays.
Express architectural routing binds consistently to explicit Input validation mappings leveraging \texttt{express-validator} sanitizing raw RESTful JSON primitives fundamentally prior to controller execution preventing structural injection vectors (NoSQL injections).
Database mutations inherently prioritize Soft Deletion patterns specifically updating an `isActive` semantic boolean value thereby preserving relational historical integrity cleanly throughout archival dependencies in place of destructive atomic deletion mappings.

\section{Comparative Analysis}
Rural Gyan successfully aggregates sophisticated features dispersed generally across disjointed solutions into one singular context optimized for low-bandwidth implementation factors natively serving Indian operational structures. 

\begin{table}[htbp]
\centering
\caption{System Capabilities Comparative Analysis}
\begin{tabularx}{\columnwidth}{@{}l|c|c|c|c|c@{}}
\toprule
\textbf{Capabilities} & \textbf{Rural Gyan} & \textbf{G-Classroom} & \textbf{Moodle} & \textbf{Zoom Edu} & \textbf{Khan Acad} \\ \midrule
WebRTC P2P Data & \textbf{Yes} & No & No & No & No \\
Socket Whiteboard & \textbf{Yes} & No & Optional & Yes & No \\
AI Tutor (Gemini) & \textbf{Yes} & No & No & No & No \\
Live Bilingual Caps & \textbf{Yes} & No & No & Paid & No \\
Teacher Mute/Vid & \textbf{Yes} & N/A & N/A & Yes & N/A \\
CSV Attendance & \textbf{Yes} & No & Plugin & Yes & No \\
Docker Deployment & \textbf{Yes} & N/A & Yes & N/A & N/A \\
Role Dashboards & \textbf{Yes} & Yes & Yes & No & Yes \\ \bottomrule
\end{tabularx}
\label{tab:comparison}
\end{table}

\section{Mobile Application Integration}
Further achieving accessibility logic, the operational web functionality extends strictly matching parity natively onto Android and iOS vectors formulated completely utilizing the \textbf{React Native} architecture compiled via \textbf{Expo}. The mobile schema implements robust stack navigation structures differentiating AuthNavigator flows seamlessly into distinct MainNavigator dashboard arrays (Profiles, VirtualClassrooms, AI Tutors). Internal functional parity establishes continuous backend syncing leveraging identical RESTful hooks via structured \texttt{apiService.js} wrapper utility networks continuously operating.

\section{Conclusion}
The successful architecture and realization of the Rural Gyan Platform distinctly demonstrates the viability executing a highly-optimized full-stack engineering strategy specifically directed to eliminate massive operational obstacles characteristic of rural educational parameters. The platform entirely realizes a fully interactive, natively bilingual, synchronized learning ecosystem deploying peer-to-peer WebRTC video execution negating the necessity for exhaustive centralized server streaming dependencies. Pairing inherently resilient local connectivity protocols with native language real-time conversion implementations immediately circumvents persistent low-bandwidth logic and massive linguistic isolation factors. The introduction natively of an AI automated tutoring vector effectively democratizes instantaneous, 24/7 educational support logic directly to traditionally marginalized student populaces establishing a formidable architecture effectively leveling operational parity securely between highly urbanized technological sectors and the vast rural expanse intrinsic to the Indian sub-continent.

\begin{thebibliography}{00}

\bibitem{webrtc}
A. Johnston and D. Burnett, ``WebRTC: APIs and RTCWEB Protocols of the HTML5 Web,'' \textit{Internet Engineering Task Force (IETF)}, RFC 7478. [Online] Available: \url{https://tools.ietf.org/html/rfc7478}

\bibitem{socketio}
Socket.IO, ``Socket.IO Documentation: Real-time application framework,'' Socket.IO, 2023. [Online] Available: \url{https://socket.io/docs/}

\bibitem{gemini}
Google, ``Gemini API Documentation: Build with Gemini 2.0 Flash,'' Google AI for Developers, 2024. [Online] Available: \url{https://ai.google.dev/docs}

\bibitem{i18next}
i18next Documentation, ``react-i18next: Internationalization for React,'' [Online] Available: \url{https://react.i18next.com/}

\bibitem{nsso}
National Sample Survey Office (NSSO), ``Key Indicators of Household Social Consumption on Education in India,'' Ministry of Statistics and Programme Implementation, Government of India, 2023.

\bibitem{docker}
Docker Inc., ``Docker Documentation: Build, Ship, and Run Any App, Anywhere,'' [Online] Available: \url{https://docs.docker.com/}

\bibitem{edtech}
R. Singh and V. Kumar, ``Evaluating the impact of digital education tools in rural India: Bandwidth constraints and pedagogical outcomes,'' \textit{IEEE Transactions on Learning Technologies}, vol. 14, no. 2, pp. 210-225, 2023.

\bibitem{webrtc_perf}
J. Garcia, et al., ``Performance Evaluation of WebRTC Peer-to-Peer vs SFU vs MCU Architectures,'' \textit{IEEE Communications Magazine}, vol. 59, no. 6, pp. 112-118, 2021.

\end{thebibliography}

\end{document}
